\documentclass{article}
\usepackage{xcolor}
\usepackage[margin=0.5in]{geometry}
\usepackage{amsmath}
\input{responseTemplate}


\begin{document}
\schmoozeeditor{Dr. Azim Eskandarian} 
\begin{buttkissing}
	\reviewerclaims For the system model, the main innovation is that the uncontrolled power loads are considered. However, in Section I, we cannot find the detailed expressions about the uncontrolled loads. Please add more references and practical example to express it, to make the manuscript more readable.
	\kissbutt Thank you for the feedback. In this paper, the uncontrolled load profile comes from historical data provided by the Utah Transit Authority in Salt Lake City, which describes the power load for an electric train as it enters and leaves the station. In practice, buses share a meter with the train power substation. If buses charge at high rates while the train accelerates out of the station, the resulting 15-minute average power spikes resulting in a dramatic increase in the monthly cost.  A discussion of how uncontrolled loads contribute to cost has been included in the introduction of the paper to increase readability.
	
	\reviewerclaims In the system model, the bus may be overlapeed in the charging station. Actually, in my opinion, the control center can schedule the charging orderly. More expressions are needed.
	\kissbutt The reviewer is correct that there will be overlap in bus schedules and that a decision must be made to determine which buses will be allowed to charge, which would very easily be given by a control center. Unfortunately, determining which bus should charge and when is non-trivial because simply scheduling buses according to their arrival time fails to account for each bus's state of charge and future availability.  The method developed in our paper accounts for these complexity (route schedules, contention at the charger, battery states of charge, etc.).  The charge schedule solution obtained using our method can be used by a control center to schedule bus charging session for all buses on all routes throughout the day.
	
	\reviewerclaims In Section III, why the bin packing approach is suitable for the needs in this manuscript?
	\kissbutt Great question. Bin packing problems have been used in a variety of resource allocation problems such as the berthing problem. In our paper, we applied the bin packing concept to encode the start and end times for charging sessions.  The width of the bin describes the duration of a charging session.  The bin packing concept is not absolutely necessary, but we adopted the bin packing concept for convenience and to connect our work with other literature on resource allocation.  This is relevant in Section III of the paper because that is where we develop constraints related to charging session start and end times and charging session duration.
	
%Section III considers the management the battery state of charge for each bus. That section develops %constraints that maintain a bus battery state of charge. which in turn drives the delivery of energy through %charge sessions. Each charge session can be thought of as an interval or ``bin'' where the bin width is thte %duration of the charging session. The minimum width is based on how much energy the bus must recieve during %the session. Therefore, because Section III includes constraints which force buses to charge, buses are %required to schedule time on a charger. In this paper, we view time on a charger as a bin whose width is %analagous to charge session duration so that the bus scheduling problem can be solved using a solution to the %bin packing problem.
	
	\reviewerclaims For the simulation, the authors should give more comparison with the current existing works, to make the effectiveness more clearly.
	\kissbutt Thank you for the feedback! Based on the reviewer's suggestion, in the results section we have added an additional comparison with other existing work. The new comparison shows how our method compares to an approach developed by Ojer et al. which focuses on managing the peak energy without considering uncontrolled loads. The method we have already compared with by He et al. focuses on minimising the cost from time of day tarrifs. Between Ojer et al. and He et al. we believe the comparisons should demonstrate the effectiveness over a range of related existing methods.
	
	\reviewerclaims The paper writing should be improved. For example, in page 9 , line 49, section ??
	\kissbutt Great catch, we have read through the paper again with a view to improve readability. This has led to a number of changes and improvements. We believe the paper has been improved. Thank you for noticing and for your feedback!
\end{buttkissing}

\begin{buttkissing}
	\reviewerclaims Simply removing references does not justify the motivation. I recommend the below three papers.
		\begin{itemize}
			\item He, J., Yan, N., Zhang, J., Wang, T., 2022. Battery electric buses charging schedule optimization considering time-of-use electricity price. Journal of Intelligent and Connected Vehicles, 4(2), 138-145
			\item Liu, Y., Wang, L., Zeng, Z., Bie, Y., 2022. Optimal charging plan for electric bus considering time-of-day electricity tariff. Journal of Intelligent and Connected Vehicles, 5(2), 123-137.
			\item Ji, J., Bie, Y.M., Zeng, Z., Wang, L., 2022. Trip energy consumption estimation for electric buses. Communication in Transportation Research 2, 100069.
		\end{itemize} 
	\kissbutt Thank you, we have incorporated the given references to better support the focus of the paper which has been shifted so that the primary motivation centers on cost savings in the presence of uncontrolled loads.
	
	\reviewerclaims The authors need to carefully describe the charging activities for each BEB bus in a day.
	\kissbutt We thank the reviewer for identifying the need to expand the discussion about daily charging activities for battery electric buses.  We have added an expanded dicsussion about this in the introductory section of the paper.
%This paper considers a traditional scenario where each bus begins the day in the station and spends the day %either on a scheduled route or at the station. Buses on route are considered unavailable and cannot charge %until they return to the station. We have included a similar explanation in the introduction section be better %explain the daily BEB activity.
  \end{buttkissing}
\end{document}
