\section{Bus Availability and Resource Contention\label{sec:4_formulation}}
The charge scheduling framework described in this paper is formulated as a constrained optimization problem that can be solved as a Mixed Integer Linear Program (MILP) of the form
\begin{equation}\label{eqn:MILP}\begin{matrix}
	\underset{\mathbf{y}}{\text{min}} \ \mathbf{y}^T\mathbf{v} \text{ subject to } \\
	\tilde{A}\mathbf{y} = \tilde{\mathbf{b}}, \ A\mathbf{y} \le \mathbf{b},
\end{matrix} \end{equation}
along with some integer constraints on elements of $\mathbf{y}$,
where $\mathbf{y}$, $\tilde{A}$, $A$, and $\mathbf{v}$ represent the solution vector, equality and inequality constraints, and cost vector respectively. In this paper, $\mathbf{y}$ is comprised of several variables, and is expressed as 
\begin{equation}\label{eqn:yDef}
	\mathbf{y} = \begin{bmatrix}
			\boldsymbol{\sigma} \\ 
			\mathbf{c}      \\ 
			\mathbf{s}      \\ 
			\mathbf{h}      \\ 
			\mathbf{k}      \\ 
			\mathbf{r}      \\ 
			\mathbf{g}      \\
			\mathbf{p}      \\ 
			\mathbf{l}      \\
			q_{\text{on}}   \\ 
			q_{\text{all}}  \\
		     \end{bmatrix},
\end{equation}
where $\boldsymbol{\sigma}$ describes on which charger a bus will charge, $\mathbf{c}$ and $\mathbf{s}$ describe time intervals over which buses charge, $\mathbf{h}$ gives the bus state of charge, $\mathbf{k}$, $\mathbf{r}$ and $\mathbf{p}$ are used to discretize the effects from $\mathbf{c}$ and $\mathbf{s}$, $\mathbf{g}$ is a slack variable for converting the effects of charging from continuous time to discrete intervals, $\mathbf{l}$ is another slack variable that prevents two buses from simultaneously being assigned to the same charger, and $q_{\text{on}}$ and $q_{\text{all}}$ represent maximum average power values that are used to compute the monthly cost of power. 
\par The cost function in \eqref{eqn:MILP} will be designed to model a realistic billing structure used by \cite{rocky_mountain_power_rocky_2021} and will minimize the cost in the presence of uncontrolled loads. Additionally, the constraints are designed to incorporate bus schedules, limit bus state of charges, and include a linear charge model calibrated on data from the Utah Transit Authority.

\subsection{Setup}
\par A solution to the bus charge problem includes both temporal and categorical information. The temporal aspect shows when and for how long a bus should charge, and is represented graphically as increasing from left to right. The vertical axis represents each category as a bus and shows how each bus charges over time as shown in Fig. \ref{fig:busTime4}.
%\input{media/4_formulation/busTime1}
\par Each bus follows a schedule of arrival and departure times, where the $i^{\text{th}}$ bus's $j^{\text{th}}$ stop begins at arrival time $a_{ij}$ and terminates at departure time $d_{ij}$ (see Fig. \ref{fig:busTime3}).  A bus can be assigned to charge anytime the bus is in the station, such that the charge start time, $c_{ij}$, is greater than or equal to $a_{ij}$, and the charge stop time, $s_{ij}$, is less than the departure time $d_{ij}$, as shown in Fig. \ref{fig:busTime3}. In the context of a MILP, the arrival and departure times $a_{ij}$ and $d_{ij}$ are known ahead of time and charge times $c_{ij}$ and $s_{ij}$ are optimization variables. 
\input{media/4_formulation/busTime3}
\subsection{Constraints\label{sec:formulation:constraint}}
The relationship between the arrival, departure, and charge intervals for the $i^{\text{th}}$ bus at the $j^{\text{th}}$ stop can be expressed as a set of inequality constraints such that
\begin{equation}\begin{aligned}
	a_{ij} &\le c_{ij} \\
	c_{ij} &\le s_{ij} \\
	s_{ij} &\le d_{ij}.
\end{aligned}\end{equation}
These constraints can be rewritten such that the optimization variables are on the left, the known parameters are on the right, and the relationship is ``less than'' (or standard form) such that
\begin{equation}\begin{aligned}
	-c_{ij} &\le -a_{ij}\\
	c_{ij} - s_{ij} &\le 0\\
	s_{ij} &\le d_{ij}.
\end{aligned}\end{equation}
Standard form is preferred because it is required by most solvers. Having the optimization variables on the left also allows the expression to be written using matrix notation as 
\begin{equation}\label{eqn:timeConstraint}
	\begin{bmatrix} -1 & 0 \\
	                 1 & -1 \\
		0 & 1\end{bmatrix} \begin{bmatrix} c_{ij} \\ s_{ij}\end{bmatrix} \le \begin{bmatrix}-a_{ij} \\ 0 \\ d_{ij} \end{bmatrix}.
\end{equation}
	However, because all constraints must follow the form $A\mathbf{y} = \mathbf{b}$ as shown in \eqref{eqn:MILP}, \eqref{eqn:timeConstraint} is expressed in terms of $\mathbf{y}$ such that
\begin{equation} \begin{aligned}
	\begin{bmatrix}
		-1^c_{ij} & 0 & \hdots &  0        \\
	         1^c_{ij} & 0 & \hdots & -1^d_{ij} \\
		 0        & 0 & \hdots &  1^d_{ij} \\ 
	\end{bmatrix}
	\mathbf{y} &\le 
	\begin{bmatrix}
	        -a_{ij} \\ 
		 0      \\ 
		 d_{ij} \\
	\end{bmatrix} \ \forall i,j \\
	A_1\mathbf{y} &\le \mathbf{b}_1,
\end{aligned} \end{equation}
	where $1^{c}_{ij}$ is $1$ at the index that corresponds to $c_{ij}$, $1^s_{ij}$ is $1$ at the index corresponding to $s_{ij}$, and $A_1$ and $\mathbf{b}_1$ stack the constraints given in \eqref{eqn:timeConstraint} for all $i,j$.
	\par The decision variables $s_{ij}$ and $c_{ij}$ from \eqref{eqn:timeConstraint} show when a bus must start and finish charging, but do not indicate on which charger. The variable $\boldsymbol{\sigma}$ from \eqref{eqn:yDef} is a vector of binary variables. Each element of $\boldsymbol{\sigma}$ is denoted $\sigma_{ijk}$ and is $1$ when bus $i$ charges during the $j^{\text{th}}$ stop at charger $k$. Because a bus can only charge at one charger at a time, the values in $\boldsymbol{\sigma}$ must be constrained such that
\begin{equation}
	\begin{aligned}
		\sum_k \sigma_{ijk} \le 1 \ \forall i,j
	\end{aligned}
\end{equation} 
or in standard form as 
\begin{equation} \begin{aligned}
	\begin{bmatrix}1_{ij1} & 1_{ij2} & \hdots & 1_{ijk} & 0 & \hdots \end{bmatrix} \mathbf{y} &\le \mathbf{1} \ \forall i,j\\
		A_2\mathbf{y} & \le \mathbf{b}_2,
\end{aligned} \end{equation}
where $1_{ijk}$ represents a $1$ at the location corresponding to $\sigma_{ijk}$.
	The variable $\sigma_{ijk}$ is used in several scenarios. The first is to ensure that buses without charge assignments have a charge time of zero by constraining $s_{ij}$ and $c_{ij}$ to be the same value. This is done by letting
	\begin{equation}\label{eqn:A3}\begin{aligned}
	s_{ij} - c_{ij} &\le M\sum_{k}\sigma_{ijk} \\
		\begin{bmatrix} 1_s & -1_c & -M_{\sigma_1} & \hdots & -M_{\sigma_k} \end{bmatrix}\begin{bmatrix}s_{ij} \\ c_{ij} \\ \sigma_{ij1} \\ \vdots \\ \sigma_{ijk} \end{bmatrix} &\le 0 \ \forall i,j 
\end{aligned} \end{equation}
	where $M$ is the maximum difference between $s_{ij}$ and $c_{ij}$, or the number of seconds in a day, also referred to as $\text{nTime}$, and $M_\sigma$ represents multiple values of $M$ at locations corresponding to each $\sigma_{ijk}$. The constraints in \eqref{eqn:A3} can be appropriately zero padded and stacked for all $i,j$ to form the linear expression
	\begin{equation} 
		A_3\mathbf{y} \le \mathbf{b}_3
	\end{equation}
	\par The values in $\boldsymbol{\sigma}$, $\mathbf{c}$, and $\mathbf{s}$ form a complete charge plan representation were $c_{ij}$ and $s_{ij}$ describe time periods when a bus will charge and $\sigma_{ijk}$ gives which charger to use. (see Fig. \ref{fig:busTime4}).
\input{media/4_formulation/busTime4}
	The variable $\sigma_{ijk}$ is also necessary to prevent situations where more than one bus is assigned to the same charger at the same time. Note that two buses, bus $i$ and bus $i^{'}$, can only be assigned to the same charger at the same time when when $a_{ij}$ for bus $i$ is less than $d_{i^{'}j^{'}}$ for bus $i^{'}$ as shown in Fig. \ref{fig:potentialOverlap}. Let $\mathcal{S}$ be the set of all bus-stop pairs such that $\left ((i,j), \ (i^{'},j^{'}) \right ) \in \mathcal{S}$ if overlap is possible between bus $i$ and bus $i^{'}$ during the $j$ and $j^{'}$ stops respectively. Charging overlap can be avoided by constraining $c_{i^{'}j^{'}} > s_{ij}$ {\it or} $c_{ij} > s_{i^{'}j^{'}}$ for all $\left ( ij, \ i^{'}j^{'}\right ) \in \mathcal{S}$.  
\input{media/4_formulation/potentialOverlap}
We desire to encode these constraints so that they may be included in our MILP. First, let $l_{\left( ij, \ i^{`}j^{`}\right )}$ be a binary decision variable that is $1$ when $c_{i^{'}j^{'}} > s_{ij}$, and $0$ when $c_{ij} > s_{i^{'}j^{'}}$ so that the overlap constriants can be expressed as 
	\begin{equation} \label{eqn:overlapConstraints2}\begin{aligned}
	c_{i^{`}j^{`}} - s_{ij}  &> -Ml_{\left( ij, \ i^{`}j^{`}\right )} \\
	c_{ij}-s_{i^{`}j^{`}} &>  -M(1 - l_{\left( ij, \ i^{`}j^{`}\right )}) \\
\end{aligned}\end{equation}
	Note that this constraint is only necessary when buses $i$ and $i^{'}$ are assigned to the same charger, so that both $\sigma_{i'j'k}$ and $\sigma_{ijk}$ are equal to 1 which can be done by modifying the switching technique from Eqn. \eqref{eqn:overlapConstraints2} so that the overlap constraints are trivially satisfied when either $\sigma_{i'j'k}$ or $\sigma_{ijk}$ is equal to zero. The equations in Eqn. \eqref{eqn:overlapConstraints2} can be relaxed by letting 
\begin{equation}\label{eqn:overlapConstraints3}\begin{aligned}
	c_{i^{'}j^{'}} - s_{ij} &> M\left[(\sigma_{i^{'}j^{'}k} + \sigma_{ijk}) - 2\right] - Ml_{\left( ij, \ i^{`}j^{`}\right )} \ \forall k \\
	c_{ij} - s_{i^{'}j^{'}} &> M\left[(\sigma_{i^{'}j^{'}k} + \sigma_{ijk}) - 2\right] - M(1 - l_{\left( ij, \ i^{`}j^{`}\right )})\ \forall k \\
\end{aligned}\end{equation}
so that when $(\sigma_{i^{'}j^{'}k} + \sigma_{ijk}) < 2$, \eqref{eqn:overlapConstraints3} is trivially satisfied for all values of $c_{i^{'}j^{'}}$ and $s_{ij}$ and when $\sigma_{i^{'}j^{'}k} = \sigma_{ijk} = 1$, \eqref{eqn:overlapConstraints3} simplifies to \eqref{eqn:overlapConstraints2}. Equation \eqref{eqn:overlapConstraints3} can be expressed in standard form using matrix notation as 
	\begin{equation}\label{eqn:overlapConstraints4}\begin{aligned} 
		\begin{bmatrix} 
			-1 & 0 &  0 & 1 & M & M & -M \\
			 0 & 1 & -1 & 0 & M & M &  M \\
		\end{bmatrix} 
		\begin{bmatrix}
			c_{i^{'}j^{'}}       \\ 
			s_{i^{'}j^{'}}       \\
			c_{ij}               \\
			s_{ij}               \\ 
			\sigma_{i^{'}j^{'}k} \\ 
			\sigma_{ijk}         \\
			l_{iji^{`}j^{`}}     \\
		\end{bmatrix} &\le 
		\begin{bmatrix} 
			2M \\ 
			3M \\
		\end{bmatrix} \forall k
	\end{aligned} \end{equation}
	The constraints in \eqref{eqn:overlapConstraints4} can be repeated for all $\left ( (i,j), \ (i^{'},j^{'}) \right ) \in \mathcal{S}$ and concatenated into a single matrix expression
	\begin{equation}\begin{aligned} 
		A_4\mathbf{y} & \le \mathbf{b}_4 \\
	\end{aligned} \end{equation} 
